### 2020-04-25 templates/Materials_and_methods__Machine_learning_models.Rmd
Fix typo

reg <- list(
  dat_3 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_3$MPa),
  dat_7 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_7$MPa),
  dat_14 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_14$MPa),
  dat_28 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_28$MPa),
  dat_56 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_56$MPa),
  dat_100 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_100$MPa)
)

@@

dens <- function(d, n){
  dens <- full_join(
      d$train %>%
        select(y) %>%
        mutate(Grup = g1, day = str_sub(n, 2)),
      d$test %>%
        select(y) %>%
        mutate(Grup = g2, day = str_sub(n, 2))
    )
  dens
}

@@

densities %>%
  ggplot(aes(y, fill = Grup)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~dia_f, ncol=3) +
  xlab("MPa") +
  ylab(ylabel) +
  theme_bw() +
  theme_minimal() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))
```

@@

kable(
    df_performance_reg,
    col.names = colNames6,
    escape = F,
    booktabs = T,
    caption = caption,
    linesep = "\\addlinespace",
    align = "c"
    )  %>%
  kable_styling(latex_options = c("HOLD_position"))
```

>>>>

reg <- list(
  dat_3 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_3$mpa),
  dat_7 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_7$mpa),
  dat_14 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_14$mpa),
  dat_28 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_28$mpa),
  dat_56 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_56$mpa),
  dat_100 %>% select(-c(mpa, class, id)) %>% mutate(y = dat_100$mpa)
)

@@

dens <- function(d, n){
  dens <- full_join(
      d$train %>%
        select(y) %>%
        mutate(Group = g1, day = str_sub(n, 2)),
      d$test %>%
        select(y) %>%
        mutate(Group = g2, day = str_sub(n, 2))
    )
  dens
}

@@

densities %>%
  ggplot(aes(y, fill = Group)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~day_f, ncol=3) +
  xlab("MPa") +
  ylab(ylabel) +
  theme_bw() +
  theme_minimal() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"))
```

@@

kable(
    df_performance_reg,
    col.names = colNames,
    escape = F,
    booktabs = T,
    caption = caption,
    linesep = "\\addlinespace",
    align = "c"
    )  %>%
  kable_styling(latex_options = c("HOLD_position"))
```
